Future challenges for Research Software Engineering

### 2025-05-12 future_challenges_for_RSEng.tex
Update future_challenges_for_RSEng.tex
Co-authored-by: Magnus Hagdorn <Magnus.Hagdorn@marsupium.org>

The workshop participants found that in earlier learning stages,
details of software frameworks and libraries may be intentionally hidden,
fearing a diminishing capability to handle technical complexity in research environments.
As a result, RSEs invest more effort in making individual research software components
less complex with better user experience.
This made participants worry about growing mismatch of peoples' expectations.
Participants expected an over-reliance on generative AI tools as an extreme manifestation of this issue.
No concrete examples were given on which complexities are now hidden behind abstractions.

>>>>

The workshop participants found that in earlier learning stages,
details of software frameworks and libraries may be intentionally hidden,
fearing a reduced capability to handle technical complexity in research environments.
As a result, RSEs invest more effort in making individual research software components
less complex with better user experience.
This made participants worry about growing mismatch of peoples' expectations.
Participants expected an over-reliance on generative AI tools as an extreme manifestation of this issue.
No concrete examples were given on which complexities are now hidden behind abstractions.
